Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-20 Draft/Draft20181218.Rmd
.

---
# {.tabset .tabset-fade .tabset-pills}

@@

treemap(pim1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Import Percentage on Countries",
        fontsize.title = 17,type="value",palette = "Set1")

@@

#grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
#grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
#fig.height=8, fig.width=16
```

>>>>

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# {.tabset .tabset-fade .tabset-pills}

@@

treemap(pim1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Import Percentage on Countries",
        fontsize.title = 17,type="value",palette = "Set1")
```

@@

#multiplot(plotCanEx, plotCanIm, plotRusEx, plotRusIm, cols=2)
#grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
#grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
#fig.height=8, fig.width=16
```
